Solar jet observed at the limb in SDO/SST

### 2016-04-25 paper/ms_temp_paper.tex
add the slit analysis figure

\subsection{Evolution}
Let us examine the raw evolution of jet in the time distance plot in \ref{td_fig}.
Here we have utilised the measuring tool to measure the extent of the feature in all the wavelengths in which it is visable.
We find that the overall profile of its evolution contains two distinct peaks in most wavelengths, with the exception of $17.1$ nm.
The first peak comes at $~07:37$ before a decrease in size and subsequent secondary expansion to its maximum length in H$\alpha$ and $30.4$ nm at approximately $07:49$.

@@

path_131 = manager.data_file('jet_picks/131_records.pik')
path_171 = manager.data_file('jet_picks/171_records.pik')
path_211 = manager.data_file('jet_picks/211_records.pik')
path_304 = manager.data_file('jet_picks/304_records.pik')
path_335 = manager.data_file('jet_picks/335_records.pik')
ha_path = manager.data_file('jet_picks/H_alpha_records.pik')

@@

>>>>

\subsection{Evolution}
Let us examine the raw evolution of jet in the time distance plot in \ref{td_fig}.
Here we have utilised the measuring tool to measure the extent of the feature in all the wavelengths in which it is visable.
We find that the overall profile of its evolution contains two distinct peaks in most wavelengths, with the exception of $17.1$ nm.
The first peak comes at $~07:37$ before a decrease in size and subsequent secondary expansion to its maximum length in H$\alpha$ and $30.4$ nm at approximately $07:49$.
This strongly implies that there is a second reconnection event in which a new material is accelerated into the atmosphere.
As such let us turn to the CRISP instrument again.

With its higher resolution, a slit based analysis of the jet can be observed in

@@

path_131 = manager.data_file('jet_picks/131_records.pik')
path_171 = manager.data_file('jet_picks/171_records.pik')
path_211 = manager.data_file('jet_picks/211_records.pik')
path_304 = manager.data_file('jet_picks/304_records.pik')
path_335 = manager.data_file('jet_picks/335_records.pik')
ha_path = manager.data_file('jet_picks/H_alpha_records.pik

@@

\begin{pycode}[SST_slit]
import numpy as np
import sunpy.cm
import matplotlib.pyplot as plt

sst_slit_path = manager.data_file('2016-01-22 14:59:58.507931.npz')

afile = np.load(sst_slit_path)
data = afile['arr2']

fig = plt.figure()
plt.imshow(np.rot90(data[3]), , cmap='cubehelix', aspect='auto')
plt.xlabel('Time in SST cadence (7.7 s)')
plt.ylabel('Distance along the slit')
sst_slit_fig = manager.save_figure('sst-slit', fig)
sst_slit_fig.figure_width = \columnwidth
sst_slit_fig.caption = 'CRISP/SST H alpha core line slit analysis.'
\end{pycode}
